Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-05-27 paper.tex
added more the bib and responses

Aside from this extension of Mackenthun's algorithm, the primary purpose of this paper is to analyse the least squares estimators of carrier phase and amplitude obtained by minimising~\eqref{eq:LSdefn}.  In the literature, analytic study of non-data-aided estimators of carrier phase has primarily involved the derivation of Cram\'{e}r-Rao lower bounds under the assumption that the noise $\{w_i\}$ is complex Gaussian distributed~\cite{Delmas_exact_crb_psk_2008,950345,Steendam_lowsnr_crb_2001,Cowley_crbs_phase_freq_1996,DAndrea_modified_bounds_1994}.  The bounds themselves are often complicated to compute and analyse and for this reason it is common to make approximations, known as \emph{modified} Cram\'{e}r-Rao bounds~\cite{DAndrea_modified_bounds_1994,Pollok_mckilliam_crb_cpm_2013}, or to analyse bounds that are valid asymptotically as the noise variance increases to infinity or decreases to zero~\cite{Moeneclaey_limit_crbs_1998,Steendam_lowsnr_crb_2001,Delmas_exact_crb_psk_2008}.  %To the authors' knowledge, all of the existing bounds are applicable only in the fully non-data-aided case or in the completely data aided case, that is, when either no pilot symbols exist, or when no data symbols exist.  Deriving bounds for the common practical scenario where there is a mixture of pilot and data symbols might be possible, but would further complicate already complicated bounds.

@@

The proof of Theorem~\ref{thm:consistency} hinges on Lemmas \ref{lem:convtoexpGlamL} to~\ref{lem:GLtoG0}, which can be found in the appendix.
Substituting $\{ \hat{d}_i(\theta), i \in D \}$ from~\eqref{eq:hatdfinxtheta} into~\eqref{eq:LSallparams} we obtain $LS$ minimised with respect to the data symbols,
 \begin{align*}
LS(\rho, \theta) &=\sum_{i \in P} \abs{ y_i - \rho e^{j\theta} p_i }^2 + \sum_{i \in D} \abs{ y_i - \rho e^{j\theta} \hat{d_i}(\theta) }^2 \\
&= A - \rho Z(\theta) - \rho Z^*(\theta) + L \rho^2,
\end{align*}
where
\[
Z(\theta)  = \sum_{i \in P} y_i e^{-j\theta} p_i^* + \sum_{i \in D} y_i e^{-j\theta} \hat{d}_i^*(\theta),
\]
and $Z^*(\theta)$ is the conjugate of $Z(\theta)$.  Differentiating with respect to $\rho$ and setting the resulting expression to zero gives the least squares estimator of $\rho_0$ as a function of $\theta$,
\begin{equation}\label{eq:hatrhoZ}
\hat{\rho}(\theta) = \frac{Z(\theta) + Z^*(\theta)}{2L} = \frac{1}{L}\Re(Z(\theta)).
\end{equation}
%where $\Re(\cdot)$ denotes the real part.  %Since $\hat{\rho}(\theta)$ is nonnegative it follows that $\Re(Z(\theta))$ is nonnegative for all $\theta \in [-\pi, \pi)$.  
Substituting this expression into $LS(\rho, \theta)$ gives $LS$ minimised with respect to $\rho$ and the data symbols,
\[
LS(\theta) = A - \frac{1}{L}\Re(Z(\theta))^2.
\]
%We again abuse notation by reusing $LS$, but this should not cause confusion as $LS(\rho,\theta)$ and $LS(\theta)$ are easily told apart by their inputs.  
By definition the amplitude $\rho_0$ and its estimator $\hat{\rho}$ are positive.  However, $\hat{\rho}(\theta) = \Re(Z(\theta))$ may take negative values for some $\theta \in [-\pi,\pi)$.  %In this case we would replace $\theta$ with $\fracpart{\theta + \phi}$ and $\hat{\rho}(\theta)$ with $-\hat{\rho}(\theta)$ and observe that
%\[
%LS(\rho,\theta) = LS(-\rho, \fracpart{\theta + \pi})
%\]
The least square estimator $\hat{\theta}$ of $\theta_0$ is the minimiser of $LS(\theta)$ under the constraint $\hat{\rho}(\theta) = \Re(Z(\theta)) > 0$.  Equivalently $\hat{\theta}$ is the maximiser of $\Re(Z(\theta))$ with no constraints required.

@@

The proof of Theorem~\ref{thm:normality} hinges on Lemmas \ref{lem:diffatlambdaL} to~\ref{lem:XL}, which can be found in the appendix.  We first prove the asymptotic normality of $\sqrt{L} \hat{\lambda}_L$.  Once this is done we will be able to prove the normality of $\sqrt{L} \hat{m}_L$.  Recall that $\hat{\lambda}_L$ is the maximiser of the function $G_L$ defined in~\eqref{eq:GLdefn}.  The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at multiples of $\tfrac{\pi}{M}$.  This prevents the use of standard approaches to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989,van2009empirical}.  However, Lemma~\ref{lem:diffatlambdaL} shows that the derivative $G_L^\prime$ does exist and is equal to zero at $\hat{\lambda}_L$.  %Similar properties have been used by some of the present authors to analyse the behaviour of polynomial-phase estimators~\cite{McKilliam_LSU_polyest_part_arxiv_2012}.  %\cite{McKilliam_LSU_polyest_part1_2012,McKilliam_LSU_polyest_part2_2012}.
Define the function
\begin{equation}\label{eq:RLdef}
R_L(\lambda) = \frac{1}{L} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\lambda + \Phi_i}.
\end{equation}
Whenever $G_L(\lambda)$ is differentiable $G_L^\prime(\lambda) = R_L(\lambda)$ and so $R_L(\hat{\lambda}_L) = G_L^\prime(\hat{\lambda}_L) = 0$ by Lemma~\ref{lem:diffatlambdaL}.  Define the function 
\[
Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)
\]
and write
\begin{align*}
0 &= R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) + Q_L(\hat{\lambda}_L) \\
&= \sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) + \sqrt{L}Q_L(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q_L(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $o_P(1)$ denotes a sequence of random variables converging in probability to zero as $L \rightarrow \infty$, and $p,d$ and $H$ are defined in the statement of Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = \sqrt{L} R_L(0) + o_P(1).
\]
It follows from the three equations above that,
\[
0 = \sqrt{L}R_L(0) + \sqrt{L} \hat{\lambda}_L \big( p + Hd  + o_P(1) \big) + o_P(1)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L =  -\frac{\sqrt{L}R_L(0)}{p + Hd  + o_P(1)} + o_P(1).
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$ where $A_1$ and $A_2$ are defined in the statement of Theorem~\ref{thm:normality}.  It follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{pA_1 + dA_2}{(p + Hd)^2}.
\]

@@

Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} show the sample mean square error (MSE) of the phase estimator when $M=2,4,8$ with $L=4096$ and for varying proportions of pilot symbols $\abs{P} = 0, \tfrac{L}{32}, \tfrac{L}{8}, \tfrac{L}{2}, L$.  When $\abs{P} \neq 0$ the mean square error is computed as $\tfrac{1}{T}\sum_{i=1}^T\sfracpart{\hat{\theta}_i - \theta_0}_\pi^2$.  Otherwise, when $\abs{P}=0$ the mean square error is computed as $\tfrac{1}{T}\sum_{i=1}^T\sfracpart{\hat{\theta}_i - \theta_0}^2$ as in~\cite{McKilliam_leastsqPSKnoncoICASSP_2012}.  The dots, squares, circles and crosses are the results of Monte-Carlo simulations with the least square estimator.  The solid lines are the estimator MSEs predicted by Theorem~\ref{thm:normality}.   %(and by Theorem~2 from~\cite{McKilliam_leastsqPSKnoncoICASSP_2012} when $\abs{P} = 0$).  
The prediction is made by dividing the asymptotic covariance matrix by $L$.  The theorem accurately predicts the behaviour of the phase estimator when $L$ is sufficiently large.  As the SNR decreases the variance of the phase estimator approaches that of the uniform distribution on $[-\pi, \pi)$ when $\abs{P} \neq 0$, and the uniform distribution on $[-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ when $\abs{P}=0$~\cite{McKilliam_leastsqPSKnoncoICASSP_2012}.  As the SNR increases the variance of the estimators converge to that of the estimator where all symbols are pilots, i.e. $\abs{P} = L$.

@@

Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} also display the sample MSE of the non-data-aided phase estimator of Viterbi and Viterbi~\cite{ViterbiViterbi_phase_est_1983}.  This estimator requires selection of a function $F$ that transforms the amplitude of each sample prior to the final estimation step.  % (see equation (2) in~\cite{ViterbiViterbi_phase_est_1983}).  
Viterbi and Viterbi propose several viable alternatives, from which we have chosen $F(x) = 1$.  The Viterbi and Viterbi estimator is only applicable in the non-data-aided setting, i.e. when $\abs{P} = 0$.  The sample MSE of the least squares estimator (when $\abs{P} = 0$) and the Viterbi and Viterbi estimator is similar.  The least squares estimator appears slightly more accurate for some values of SNR.
Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} also display the non-data aided Cram\'{e}r-Rao lower bound (CRB) for carrier phase given in~\cite{Cowley_crbs_phase_freq_1996,950345}.  These CRBs are derived for the non-data aided setting and are only valid for estimators that do not make use of pilot symbols, i.e., $\abs{P}=0$.

@@

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM2-1.mps}
		\caption{Amplitude estimator versus SNR for BPSK with $L=2048$}
		\label{fig:plotampBPSK}
\end{figure}

% \begin{figure}[p]
% 	\centering
% 		\includegraphics[width=\linewidth]{code/data/plotM4-1.mps}
% 		\caption{Unbiased amplitude error versus SNR for QPSK.}
% 		\label{fig:plotampQPSK}
% \end{figure}

% \begin{figure}[p]
% 	\centering
% 		\includegraphics[width=\linewidth]{code/data/plotM8-1.mps}
% 		\caption{Unbiased amplitude error versus SNR for $8$-PSK.}
% 		\label{fig:plotamp8PSK}
% \end{figure}

%\begin{figure}[tp]
%	\centering
%		\includegraphics[width=\linewidth]{code/data/plotM2-3.mps}
%		\caption{Phase error versus SNR for BPSK.}
%		\label{fig:plotphase}
%\end{figure}

>>>>

Aside from this extension of Mackenthun's algorithm, the primary purpose of this paper is to analyse the least squares estimators of carrier phase and amplitude obtained by minimising~\eqref{eq:LSdefn}.  In the literature, analytic study of non-data-aided estimators of carrier phase has primarily involved the derivation of Cram\'{e}r-Rao lower bounds under the assumption that the noise $\{w_i\}$ is complex Gaussian distributed~\cite{Delmas_exact_crb_psk_2008,950345,Steendam_lowsnr_crb_2001,Cowley_crbs_phase_freq_1996,DAndrea_modified_bounds_1994}.  The bounds themselves are often complicated to compute and analyse and for this reason it is common to make approximations, known as \emph{modified} Cram\'{e}r-Rao bounds~\cite{DAndrea_modified_bounds_1994,Pollok_mckilliam_crb_cpm_2013}, or to analyse bounds that are valid asymptotically as the noise variance increases to infinity or decreases to zero~\cite{Moeneclaey_limit_crbs_1998,Steendam_lowsnr_crb_2001,Delmas_exact_crb_psk_2008}.  %To the authors' knowledge, all of the existing bounds are applicable only in the fully non-data-aided case or in the completely data-aided case, that is, when either no pilot symbols exist, or when no data symbols exist.  Deriving bounds for the common practical scenario where there is a mixture of pilot and data symbols might be possible, but would further complicate already complicated bounds.

@@

The proof of Theorem~\ref{thm:consistency} relies on Lemmas \ref{lem:convtoexpGlamL} to~\ref{lem:GLtoG0}, which can be found in the appendix.
Substituting $\{ \hat{d}_i(\theta), i \in D \}$ from~\eqref{eq:hatdfinxtheta} into~\eqref{eq:LSallparams} we obtain $LS$ minimised with respect to the data symbols,
 \begin{align*}
LS(\rho, \theta) &=\sum_{i \in P} \abs{ y_i - \rho e^{j\theta} p_i }^2 + \sum_{i \in D} \abs{ y_i - \rho e^{j\theta} \hat{d_i}(\theta) }^2 \\
&= A - \rho Z(\theta) - \rho Z^*(\theta) + L \rho^2,
\end{align*}
where
\[
Z(\theta)  = \sum_{i \in P} y_i e^{-j\theta} p_i^* + \sum_{i \in D} y_i e^{-j\theta} \hat{d}_i^*(\theta),
\]
and $Z^*(\theta)$ is the conjugate of $Z(\theta)$.  Differentiating with respect to $\rho$ and setting the resulting expression to zero gives the least squares estimator of $\rho_0$ as a function of $\theta$,
\begin{equation}\label{eq:hatrhoZ}
\hat{\rho}(\theta) = \frac{Z(\theta) + Z^*(\theta)}{2L} = \frac{1}{L}\Re(Z(\theta)).
\end{equation}
%where $\Re(\cdot)$ denotes the real part.  %Since $\hat{\rho}(\theta)$ is nonnegative it follows that $\Re(Z(\theta))$ is nonnegative for all $\theta \in [-\pi, \pi)$.  
Substituting this expression into $LS(\rho, \theta)$ gives $LS$ minimised with respect to $\rho$ and the data symbols,
\[
LS(\theta) = A - \frac{1}{L}\Re(Z(\theta))^2.
\]
%We again abuse notation by reusing $LS$, but this should not cause confusion as $LS(\rho,\theta)$ and $LS(\theta)$ are easily told apart by their inputs.  
By definition the amplitude $\rho_0$ and its estimator $\hat{\rho}$ are positive.  However, $\hat{\rho}(\theta) = \Re(Z(\theta))$ may take negative values for some $\theta \in [-\pi,\pi)$.  %In this case we would replace $\theta$ with $\fracpart{\theta + \phi}$ and $\hat{\rho}(\theta)$ with $-\hat{\rho}(\theta)$ and observe that
%\[
%LS(\rho,\theta) = LS(-\rho, \fracpart{\theta + \pi})
%\]
The least square estimator $\hat{\theta}$ of $\theta_0$ is the minimiser of $LS(\theta)$ under the constraint $\hat{\rho}(\theta) = \Re(Z(\theta)) > 0$.  Equivalently $\hat{\theta}$ is the maximiser of $\Re(Z(\theta))$ with no constraints required.

@@

The proof of Theorem~\ref{thm:normality} relies on Lemmas \ref{lem:diffatlambdaL} to~\ref{lem:XL}, which can be found in the appendix.  We first prove the asymptotic normality of $\sqrt{L} \hat{\lambda}_L$.  Once this is done we will be able to prove the normality of $\sqrt{L} \hat{m}_L$.  Recall that $\hat{\lambda}_L$ is the maximiser of the function $G_L$ defined in~\eqref{eq:GLdefn}.  The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at multiples of $\tfrac{\pi}{M}$.  This prevents the use of standard approaches to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989,van2009empirical}.  However, Lemma~\ref{lem:diffatlambdaL} shows that the derivative $G_L^\prime$ does exist and is equal to zero at $\hat{\lambda}_L$.  %Similar properties have been used by some of the present authors to analyse the behaviour of polynomial-phase estimators~\cite{McKilliam_LSU_polyest_part_arxiv_2012}.  %\cite{McKilliam_LSU_polyest_part1_2012,McKilliam_LSU_polyest_part2_2012}.
Define the function
\begin{equation}\label{eq:RLdef}
R_L(\lambda) = \frac{1}{L} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\lambda + \Phi_i}.
\end{equation}
Whenever $G_L(\lambda)$ is differentiable $G_L^\prime(\lambda) = R_L(\lambda)$ and so $R_L(\hat{\lambda}_L) = G_L^\prime(\hat{\lambda}_L) = 0$ by Lemma~\ref{lem:diffatlambdaL}.  Define the function 
\[
Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)
\]
and write
\begin{align*}
0 &= R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) + Q_L(\hat{\lambda}_L) \\
&= \sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) + \sqrt{L}Q_L(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q_L(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $o_P(1)$ denotes a sequence of random variables converging in probability to zero as $L \rightarrow \infty$, and $p,d$ and $H$ are defined in the statement of Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( R_L(\hat{\lambda}_L) - Q_L(\hat{\lambda}_L) \big) = \sqrt{L} R_L(0) + o_P(1).
\]
It follows from the three equations above that,
\[
0 = \sqrt{L}R_L(0) + \sqrt{L} \hat{\lambda}_L \big( p + Hd  + o_P(1) \big) + o_P(1)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L =  -\frac{\sqrt{L}R_L(0)}{p + Hd  + o_P(1)} + o_P(1).
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$ where $A_1$ and $A_2$ are defined in the statement of Theorem~\ref{thm:normality}.  It follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{pA_1 + dA_2}{(p + Hd)^2}.
\]

@@

Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} show the sample mean square error (MSE) of the phase estimator when $M=2,4,8$ with $L=4096$ and for varying proportions of pilot symbols $\abs{P} = 0, \tfrac{L}{32}, \tfrac{L}{8}, \tfrac{L}{2}, L$.  When $\abs{P} \neq 0$ the mean square error is computed as $\tfrac{1}{T}\sum_{i=1}^T\sfracpart{\hat{\theta}_i - \theta_0}_\pi^2$.  Otherwise, when $\abs{P}=0$ the mean square error is computed as $\tfrac{1}{T}\sum_{i=1}^T\sfracpart{\hat{\theta}_i - \theta_0}^2$ as in~\cite{McKilliam_leastsqPSKnoncoICASSP_2012}.  The dots, squares, circles and crosses are the results of Monte-Carlo simulations with the least square estimator.  The solid lines are the estimator MSEs predicted by Theorem~\ref{thm:normality}.   %(and by Theorem~2 from~\cite{McKilliam_leastsqPSKnoncoICASSP_2012} when $\abs{P} = 0$).  
The prediction is made by dividing the asymptotic covariance matrix by $L$.  The theorem accurately predicts the behaviour of the phase estimator when SNR is sufficiently large.  As the SNR decreases the variance of the phase estimator approaches that of the uniform distribution on $[-\pi, \pi)$ when $\abs{P} \neq 0$, and the uniform distribution on $[-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ when $\abs{P}=0$~\cite{McKilliam_leastsqPSKnoncoICASSP_2012}.  As the SNR increases the variance of the estimators converge to that of the estimator where all symbols are pilots, i.e. $\abs{P} = L$.

@@

Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} also display the sample MSE of the non-data-aided phase estimator of Viterbi and Viterbi~\cite{ViterbiViterbi_phase_est_1983}.  This estimator requires selection of a function $F$ that transforms the amplitude of each sample prior to the final estimation step.  % (see equation (2) in~\cite{ViterbiViterbi_phase_est_1983}).  
Viterbi and Viterbi propose several viable alternatives, from which we have chosen $F(x) = 1$.  The Viterbi and Viterbi estimator is only applicable in the non-data-aided setting, i.e. when $\abs{P} = 0$.  The sample MSE of the least squares estimator (when $\abs{P} = 0$) and the Viterbi and Viterbi estimator is similar.  The least squares estimator appears slightly more accurate for some values of SNR.
Figures~\ref{fig:plotphaseBPSK},~\ref{fig:plotphaseQPSK}~and~\ref{fig:plotphase8PSK} also display the non-data-aided Cram\'{e}r-Rao lower bound (CRB) for carrier phase given in~\cite{Cowley_crbs_phase_freq_1996,950345}.  These CRBs are derived for the non-data-aided setting and are only valid for estimators that do not make use of pilot symbols, i.e., $\abs{P}=0$.

@@

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM2-1.mps}
		\caption{Amplitude estimator versus SNR for BPSK with $L=4096$.}
		\label{fig:plotampBPSK}
\end{figure}

\begin{figure}[p]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM4-1.mps}
		\caption{Amplitude error versus SNR for QPSK with $L=4096$.}
		\label{fig:plotampQPSK}
\end{figure}

\begin{figure}[p]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM8-1.mps}
		\caption{Amplitude error versus SNR for $8$-PSK with $L=4096$.}
		\label{fig:plotamp8PSK}
\end{figure}

### 2014-05-27 response2.tex
added more the bib and responses

\item \textbf{Comment:} Conference papers: location missing \\
\textbf{Response:}

\item \textbf{Comment:} Some journal papers: month of publication missing \\
\textbf{Response:}

\item \textbf{Comment:} [8] \dots IEEE Commun. Letters \dots \\
\textbf{Response:}

\item \textbf{Comment:} [31] N. Noels, V. Lottici, \dots \\
\textbf{Response:}

@@

\item \textbf{Comment:} p. 3: ``the situations is'' --> drop `s' at the end of situations \\
\textbf{Response:} Fixed.

@@

\item \textbf{Comment:} in general, I find the numerical results section rather short \\
\textbf{Response:}

@@

\item \textbf{Comment:} p. 18, first sentence: ``when $L$ is sufficiently large'' $\to$ in these figures the value of $L$ is fixed, should this be ``when the SNR is sufficiently large''  \\
\textbf{Response:}

\item \textbf{Comment:} p. 18, first sentence: a qualitative explanation for the fact the theory and simulations diverge at low SNR would be appreciated  \\
\textbf{Response:}

\item \textbf{Comment:} p.18, last sentence of first paragraph: ``non-data aided'' $\to$ should be ``non-data-aided''  \\
\textbf{Response:}

\item \textbf{Comment:}  although the most important contribution of the paper is with respect to the biased amplitude estimate, only 1 figure is presented for amplitude estimation, namely for L=2048 and BPSK --> this seems not well balanced  \\
\textbf{Response:}

>>>>

\item \textbf{Comment:} Conference papers: location missing \\
\textbf{Response:} The location of conferences has been added.

\item \textbf{Comment:} Some journal papers: month of publication missing \\
\textbf{Response:} The month has been added whenever it was available in the original publication.

\item \textbf{Comment:} [8] \dots IEEE Commun. Letters \dots \\
\textbf{Response:} Fixed.

\item \textbf{Comment:} [31] N. Noels, V. Lottici, \dots \\
\textbf{Response:} Fixed.

@@

\item \textbf{Comment:} p. 3: ``the situations is'' $\to$ drop `s' at the end of situations \\
\textbf{Response:} Fixed.

@@

\item \textbf{Comment:} in general, I find the numerical results section rather short \\
\textbf{Response:} We have greatly expanded the simulation section. BLERG: this includes \dots ref to below.

@@

\item \textbf{Comment:} p. 18, first sentence: ``when $L$ is sufficiently large'' $\to$ in these figures the value of $L$ is fixed, should this be ``when the SNR is sufficiently large''  \\
\textbf{Response:} Fixed.

\item \textbf{Comment:} p. 18, first sentence: a qualitative explanation for the fact the theory and simulations diverge at low SNR would be appreciated  \\
\textbf{Response:} BLERG: Added a reference to Tazras crb paper.

\item \textbf{Comment:} p.18, last sentence of first paragraph: ``non-data aided'' $\to$ should be ``non-data-aided''  \\
\textbf{Response:} Fixed.

\item \textbf{Comment:}  although the most important contribution of the paper is with respect to the biased amplitude estimate, only 1 figure is presented for amplitude estimation, namely for $L=2048$ and BPSK $\to$ this seems not well balanced  \\
\textbf{Response:} Figures have been added showing the amplitude estimation error for BSPK, QPSK, and 8-PSK.
